### 2019-01-20 journal/experiments.tex
more text

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering with our metrics, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  We confirm the conclusion \cite{PLDI13} that clustering is of limited value in fuzzer taming.
% (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  %A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

@@

The APFD (Average Percent Faults Detected) values in the graphs are based on the measure  introduced by Rothermel et al. for evaluating test case prioritization methods \cite{APFD}.  APFD is a somewhat better summary of results than the raw curve areas used for evaluation in previous work \cite{PLDI13}.  APFD, as the name suggests, measures the percent of all faults discovered at the ``average'' point on the curve, by comparing the curve's area to an ideal curve, with interpolation.  A simpler (but less informative) way to compare the curves is to note that the mutation-based metric's curve is above the best previous curve at 60\% of data points.
%\footnote{The details of APFD calculation are slightly involved, and the interpolation and perfect curve are not exact fits for fuzzer taming; nonetheless the basic method summarizes curves fairly well and is standard in the testing literature for similar problems \cite{issta14}.}.

@@

\comment{
Results are reported as absolute ranks, rather than more sophisticated \cite{MUSE} localization evaluations because our localizations do not assign suspiciousness scores, only rankings, and in accord with the proposal of Parnin and Orso that only localizations ranking a fault in the top few statements may be useful to users \cite{AutoHelp}.  We expect users to examine coverage changes and mutants.  Blind, unaided pointers to portions of compiler code without more semantic information about why the statement is suspicious seem unlikely to work well, based on our experience with complex compiler faults, and the results of Parnin and Orso \cite{AutoHelp}.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{comment}                                               %
% \begin{figure}                                                %
% {\scriptsize                                                  %
% \begin{code}                                                  %
% {\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
% ...                                                           %
% <             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
% <         \} else \{                                          %
% <             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
% <         \}                                                  %
% ...                                                           %
% <                   a->avail = (jsuword)sp;                   %
% <               \}                                            %
% ...                                                           %
% ---                                                           %
% >         RESTORE\_SP(fp);                                    %
% ...                                                           %
% {\bf Mutant information:}                                     %
% Failure repaired by 148 mutants.                              %
% ...                                                           %
% \#3: delete statement mutant of jsinterp.c:944:               %
%                                                               %
%             vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
%         \} else \{                                            %
% /*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
%         \}                                                    %
%                                                               %
% {\bf Coverage change information:}                            %
% ...                                                           %
% \#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:      %
%                    a->avail = (jsuword)sp; /* ADDED */        %
% \end{code}                                                    %
% }                                                             %
% \caption{Patch and explanation for fault 115}                 %
% %\vspace{-0.18in}                                             %
% \label{fig:explain}                                           %
% \end{figure}                                                  %
% \end{comment}                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{comment}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% \subsubsection{Error Explanation}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% Figure \ref{fig:explain} shows part of the patch for SpiderMonkey fault 115, and the {\bf Coverage} and {\bf Repair} outputs that successfully localize the fault (the 6th coverage change output, and the 3rd mutant output), to give some idea of the information our methods present.  For {\bf Coverage}, it is surprising that the sixth highest ranked change only appeared in 5 of 148 repairs. This change ranked high out of thousands of changes because it was unusual, appearing for only 10 repairs in the entire SpiderMonkey analysis.  %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% The precise form an explanation based on our techniques should take is not clear.  One possibility, suggested by the results here, is a method focused on repairs, but using common coverage changes.  For each repairing mutant, in rank order, the highest ranking coverage changes for that mutant could also be shown, to give an idea of unusual (and potentially localizing) changes induced by repair.                                                                                                                                          %
% \end{comment}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering with our metrics, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  We confirm the conclusion \cite{PLDI13} that clustering (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

@@

The APFD (Average Percent Faults Detected) values in the graphs are based on the measure  introduced by Rothermel et al. for evaluating test case prioritization methods \cite{APFD}.  APFD is a somewhat better summary of results than the raw curve areas used for evaluation in previous work \cite{PLDI13}.  APFD, as the name suggests, measures the percent of all faults discovered at the ``average'' point on the curve, by comparing the curve's area to an ideal curve, with interpolation.  A simpler (but less informative) way to compare the curves is to note that the mutation-based metric's curve is above the best previous curve at 60\% of data points\footnote{The details of APFD calculation are slightly involved, and the interpolation and perfect curve are not exact fits for fuzzer taming; nonetheless the basic method summarizes curves fairly well and is standard in the testing literature for similar problems \cite{issta14}.}.

@@

Results are reported as absolute ranks, rather than more sophisticated \cite{MUSE} localization evaluations because our localizations do not assign suspiciousness scores, only rankings, and in accord with the proposal of Parnin and Orso that only localizations ranking a fault in the top few statements may be useful to users \cite{AutoHelp}.  We expect users to examine the mutants and consider how they help avoid the fault.  Blind, unaided pointers to portions of compiler code without more semantic information about why the statement is suspicious seem unlikely to work well, based on our experience with complex compiler faults, and the results of Parnin and Orso \cite{AutoHelp}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}                                               %
\begin{figure}                                                %
{\scriptsize                                                  %
\begin{code}                                                  %
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
...                                                           %
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
<         \} else \{                                          %
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
<         \}                                                  %
...                                                           %
<                   a->avail = (jsuword)sp;                   %
<               \}                                            %
...                                                           %
---                                                           %
>         RESTORE\_SP(fp);                                    %
...                                                           %
{\bf Mutant information:}                                     %
Failure repaired by 148 mutants.                              %
...                                                           %
\#3: delete statement mutant of jsinterp.c:944:               %
                                                              %
            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
        \} else \{                                            %
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
        \}                                                    %
                                                              %
\end{code}                                                    %
}                                                             %
\caption{Patch and explanation for fault 115}                 %
%\vspace{-0.18in}                                             %
\label{fig:explain}                                           %
\end{figure}                                                  %
\end{comment}                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{comment}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% \subsubsection{Error Explanation}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
 Figure \ref{fig:explain} shows part of the patch for SpiderMonkey fault 115, and the {\bf Repair} output that successfully localizes the fault (the 3rd mutant output), to give some idea of the information our method presents.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-01-20 journal/localizations.tex
more text

\comment{
By definition, when a mutant repairs a test case, it changes the
behavior of the test.  In some cases, this behavioral change is
limited to changes in program state and data values.  However, the
vast majority of mutant repairs also modify the code coverage of a
test; in our experiments, there were no repairs that did not change
coverage.  If a fault can be avoided by, for example, disabling a
problematic optimization in a compiler, this naturally leads to
changed coverage.  If the fault is due to a bad conditional, where a
program path should include additional code, the repair will often
change the execution to include the omitted code.  As a localization
for a fault, then, we can examine the source statements whose
  coverage changed most often in repairs.  Early experiments with this
  approach showed that a useful coverage change localization must  account for the frequency of a
change.  Some coverage changes are extremely common across all
failures, faults, and repairing mutants,
and therefore likely not related to any specific fault.

That is, the ranking is based on the number of times a statement's
coverage changes its value (covered or not covered) from the original
execution of $f$ in executions of mutants that repair $f$.  Changes are weighted by their inverse frequency over all
failures and all mutants.
Higher values for $r$ result in a higher ranking (more likely to
be faulty).  
%Computing $U$ accounts for the fact that in our
%experiments, a few statements were added or removed for every single
%r
}
Repairing mutants can be used for localization and
explanation.  While few will be equivalent to actual fixes, they
will sometimes overlap the incorrect code, and will often be closely
related to incorrect code, semantically.  Since some tests are
repaired by a large number of mutants, it is important to rank the
mutants to produce a localization.  Based on the onion-ring model proposed above, this is simple: each mutant is ranked as
a localization/explanation based on the \emph{most distant failure it also
  repairs.}  If a given mutant only repairs failures that have similar
repair vectors to the test case being localized, it will be highly
ranked.  If it repairs even one very dissimilar failure, then it will
be considered a poor localization.

@@

\comment{
The coverage localization also provides a kind of explanation, though
a less direct one.  For any
interesting line of code in the coverage-change-based localization,
the user can investigate a particular instance of the change,
by selecting a single mutant and stepping through the execution of the
failing test case in a debugger to the point of change.  The user can also
browse through all mutants that produce this coverage change for the test
case.

Another advantage over many statistical approaches to
localization is that our methods are not potentially confused in
settings with multiple faults.  Each localization/explanation is based
on a single failing test case, which in most cases fails due to only one
fault.  In fact, other faults help both methods rank localizations.}

>>>>

%Computing $U$ accounts for the fact that in our
%experiments, a few statements were added or removed for every single
%r

Repairing mutants can be used for localization and
explanation.  While few will be equivalent to actual fixes, they
will sometimes overlap the incorrect code, and will often be closely
related to incorrect code, semantically.  Since some tests are
repaired by a large number of mutants, it is important to rank the
mutants to produce a localization.  Based on the onion-ring model proposed above, this is simple: each mutant is ranked as
a localization/explanation based on the \emph{most distant failure it also
  repairs.}  If a given mutant only repairs failures that have similar
repair vectors to the test case being localized, it will be highly
ranked.  If it repairs even one very dissimilar failure, then it will
be considered a poor localization.

@@

\subsection{Coverage-Based Localizaton}

By definition, when a mutant repairs a test case, it changes the
behavior of the test.  In some cases, this behavioral change is
limited to changes in program state and data values.  However, the
vast majority of mutant repairs also modify the code coverage of a
test; in our experiments, there were no repairs that did not change
coverage.  If a fault can be avoided by, for example, disabling a
problematic optimization in a compiler, this naturally leads to
changed coverage.  If the fault is due to a bad conditional, where a
program path should include additional code, the repair will often
change the execution to include the omitted code.  As a localization
for a fault, then, we can examine the source statements whose
  coverage changed most often in repairs.  Early experiments with this
  approach showed that a useful coverage change localization must  account for the frequency of a
change.  Some coverage changes are extremely common across all
failures, faults, and repairing mutants,
and therefore likely not related to any specific fault.

That is, the ranking is based on the number of times a statement's
coverage changes its value (covered or not covered) from the original
execution of $f$ in executions of mutants that repair $f$.  Changes are weighted by their inverse frequency over all
failures and all mutants.
Higher values for $r$ result in a higher ranking (more likely to
be faulty).

The coverage localization also provides a kind of explanation, though
a less direct one.  For any
interesting line of code in the coverage-change-based localization,
the user can investigate a particular instance of the change,
by selecting a single mutant and stepping through the execution of the
failing test case in a debugger to the point of change.  The user can also
browse through all mutants that produce this coverage change for the test
case.

Another advantage over many statistical approaches to
localization is that our methods are not potentially confused in
settings with multiple faults.  Each localization/explanation is based
on a single failing test case, which in most cases fails due to only one
fault.  In fact, other faults help both methods rank localizations.

### 2019-01-20 journal/relatedwork.tex
more text

%There are four primary areas of related work.  First, fuzzer taming and related problems of determining the set of faults from a large set of redundant failures have been investigated in a few papers.  Second, some recent efforts to localize faults have begun to incorporate the use of program mutants, and the broader problem of fault localization has been very extensively investigated.  Program mutants have also been used in efforts to produce automatic repairs for program faults.  Finally, our work fits into the general framework of efforts to define distances between program executions.

@@

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
%The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines. \comment{, and is perhaps most similar to ours in assumptions, in particular ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  While we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults.} Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  \comment{MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure. }

>>>>

There are four primary areas of related work.  First, fuzzer taming and related problems of determining the set of faults from a large set of redundant failures have been investigated in a few papers.  Second, some recent efforts to localize faults have begun to incorporate the use of program mutants, and the broader problem of fault localization has been very extensively investigated.  Program mutants have also been used in efforts to produce automatic repairs for program faults.  Finally, our work fits into the general framework of efforts to define distances between program executions.

@@

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines. \comment{, and is perhaps most similar to ours in assumptions, in particular ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  While we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults.} Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  \comment{MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure. }
